---
title: "MLr_C7_SVM"
author: "Rice"
date: "2023-07-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("kernlab")
```

```{r}
library(kernlab)
```



```{r}
letters <- read.csv("D:/Dropbox/13 - R-WD/Letter Recognition Dataset/letter-recognition.csv",header=FALSE,stringsAsFactors = TRUE)

letters <- data.frame(letters)

names_col <- c("Letter","x-box","y-box","width","high","onpix","x-bar","y-bar","x2bar","y2bar","xybar","x2ybr","xy2br","x-ege","xegvy","y-evx","yegvx")

names(letters) <- names_col


class(letters)
head(letters)
dim(letters)
str(letters)
```
```{r}
letters_train <- letters[1:16000,]
letters_test <- letters[16001:20000,]
```
Attribute Information:
	 1.	lettr	capital letter	(26 values from A to Z)
	 2.	x-box	horizontal position of box	(integer)
	 3.	y-box	vertical position of box	(integer)
	 4.	width	width of box			(integer)
	 5.	high 	height of box			(integer)
	 6.	onpix	total # on pixels		(integer)
	 7.	x-bar	mean x of on pixels in box	(integer)
	 8.	y-bar	mean y of on pixels in box	(integer)
	 9.	x2bar	mean x variance			(integer)
	10.	y2bar	mean y variance			(integer)
	11.	xybar	mean x y correlation		(integer)
	12.	x2ybr	mean of x * x * y		(integer)
	13.	xy2br	mean of x * y * y		(integer)
	14.	x-ege	mean edge count left to right	(integer)
	15.	xegvy	correlation of x-ege with y	(integer)
	16.	y-ege	mean edge count bottom to top	(integer)
	17.	yegvx	correlation of y-ege with x	(integer)
	
```{r}


letter_classifier <- ksvm(Letter ~ ., data = letters_train, kernel = "vanilladot")

letter_classifier

```
```{r}
letter_predictions <- predict(letter_classifier, letters_test)

#letters_train <- letters[1:16000,]
#letters_test <- letters[16001:20000,]
#letter_classifier
#head(letter_predictions)
dim(letter_predictions)
# dim(letters_test)
table(letter_predictions, letters_test$Letter)

```
```{r}
agreement <- letter_predictions == letters_test$Letter
table(agreement)
prop.table(table(agreement))
```

```{r}
set.seed(12345)
letter_classifier_rbf <- ksvm(Letter ~ ., data = letters_train,kernel = "rbfdot")
letter_predictions_rbf <- predict(letter_classifier_rbf, letters_test)
agreement_rbf <- letter_predictions_rbf == letters_test$Letter
table(agreement_rbf)

prop.table(table(agreement))

```

```{r}
cost_values <- c(1, seq(from = 5, to = 40, by = 5))
accuracy_values <- sapply(cost_values, function(x) {
 set.seed(12345)
 m <- ksvm(Letter ~ ., data = letters_train,
 kernel = "rbfdot", C = x)
 pred <- predict(m, letters_test)
 agree <- ifelse(pred == letters_test$Letter, 1, 0)
 accuracy <- sum(agree) / nrow(letters_test)
 return (accuracy)
 })
plot(cost_values, accuracy_values, type = "b")
```


